Concurrent Programming with Harmony

### 2020-08-12 book/paper.tex
Latest

\section*{Exercises}
\begin{problems}
\item
Run \autoref{fig:incfixed} using (i) \texttt{synch} and (ii) \texttt{synchS}.
Report how many states were explored by Harmony for each module.
\item \label{ex:trylock} Implement \texttt{trylock}(\textit{lk}) as an additional
interface for both the \texttt{synch} and \texttt{synchS} modules.
This interface is like \texttt{lock}(\textit{lk}) but never blocks.  It
returns \texttt{True} if the lock was available (and now acquired) or \texttt{False}
if the lock was already taken.
Hint: you do not have to change the existing code.
\end{problems}

@@

\section*{Exercises}
\begin{problems}
\item Draw additional states and steps in \autoref{fig:rdwr}
for three processes.
\item \label{ex:boundlock} Using busy waiting, implement a ``bound lock'' that allows
up to \texttt{M} processes to acquire it at the same time.  A bound lock
with \texttt{M == 1} is an ordinary lock.
You should define a constant \texttt{M} and two methods:
\texttt{acquire\_bound\_lock()}
and \texttt{release\_bound\_lock()}.
\item Write a test program for your bound lock
that checks that no more than \texttt{M} processes can acquire the
bound lock.
\end{problems}

>>>>

\section*{Exercises}
\begin{problems}
\item
Run \autoref{fig:incfixed} using (i) \texttt{synch} and (ii) \texttt{synchS}.
Report how many states were explored by Harmony for each module.
\item \label{ex:xy} \autoref{fig:xy} shows a Harmony program with two variables $x$
(initially 0) and $y$ (initially 100) that can be accessed through methods
\texttt{setX} and \texttt{getXY}.  An application invariant is that \texttt{getXY}
should return a pair that sums to 100.  Add the necessary synchronization code.
\item \label{ex:trylock} Implement \texttt{trylock}(\textit{lk}) as an additional
interface for both the \texttt{synch} and \texttt{synchS} modules.
This interface is like \texttt{lock}(\textit{lk}) but never blocks.  It
returns \texttt{True} if the lock was available (and now acquired) or \texttt{False}
if the lock was already taken.
Hint: you do not have to change the existing code.
\end{problems}

\begin{figure}
\begin{code}
\harmonysource{xy}
\end{code}
\caption{$x + y = 100$.}
\label{fig:xy}
\end{figure}

@@

\section*{Exercises}
\begin{problems}
\item Draw additional states and steps in \autoref{fig:rdwr}
for three processes.
\item Optimize your solution to \autoref{ex:xy} to use reader/writer locks.
\item \label{ex:boundlock} Using busy waiting, implement a ``bound lock'' that allows
up to \texttt{M} processes to acquire it at the same time.  A bound lock
with \texttt{M == 1} is an ordinary lock.
You should define a constant \texttt{M} and two methods:
\texttt{acquire\_bound\_lock()}
and \texttt{release\_bound\_lock()}.
\item Write a test program for your bound lock
that checks that no more than \texttt{M} processes can acquire the
bound lock.
\end{problems}
